Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-03-19 paper.qmd
Plan to update the source script

```{r}
#| label: import-scripts
source("scripts/one_c_shaped_dens_structure/04_gen_error_plots.R")
source("scripts/five_gau_clusters/5_gen_model_with_tsne.R")
source("scripts/two_non_linear_diff_shaped_close_clusters/10_gen_rm_lg_plots.R")
```

>>>>

```{r}
#| label: import-scripts
source("scripts/one_c_shaped_dens_structure/04_gen_error_plots.R")
source("scripts/two_non_linear_diff_shaped_close_clusters/10_gen_rm_lg_plots.R")
```
